Implementation and comparison of register allocation to translate \lstinline!LLVM--! to x86

### 2023-11-27 article.tex
Add some benchmarks

The two primary sources are the Tiger- \cite{AppelAndrewW} and Dragonbook \cite{alma99122774374105763}, in addition to scientific publications concerning the linear scan approach.

@@

The algorithm described in \cite{AppelAndrewW} and \cite{alma99122774374105763} is based on the following equations for the live-in and live-out variables respectively:
\begin{align}
  in\left[n\right] &= use\left[n\right] \cup (out\left[n\right] - \mathit{def}\left[n\right])\\
  out\left[n\right] &= \bigcup_{s\in \mathit{succ}\left[n\right]} in\left[s\right]
\end{align}
where \(use\left[n\right]\) is the set of all dependent variables, \(def\left[n\right]\) is the set of all variables defines and \(succ\left[n\right]\) is the set of all immediate successor nodes of \(n\).

The structure of the CFG is inherently vague as both  \textit{Modern Compiler Implementation in ML} \cite{AppelAndrewW} and \textit{Compilers : Principles, Techniques, and Tools} \cite{alma99122774374105763}, while based on the same underlying % TODO: fix references
conceptions of dataflow, have different approaches to nodes of a CFG, with the former taking each individual instruction into consideration and the latter each basic block. Either of these approaches are sound

@@

\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 sha256 & -O0 & -O1 & -O2 & -O3 \\ [0.5ex] 
 \hline
 1000000 & 1 & 0.73 & 0.73 & 0.73 \\ [1ex] 
 \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 sha256 & -O0 & -O1 & -O2 & -O3 \\ [0.5ex] 
 \hline
 1000000 & 1 & 0.73 & 0.73 & 0.73 \\ [1ex] 
 \hline
\end{tabular}
\end{center}

>>>>

The two primary sources are the \textit{Modern Compiler Implementation in ML} \cite{AppelAndrewW} and Dragonbook \cite{alma99122774374105763}, in addition to scientific publications concerning the linear scan approach.

@@

The algorithm described in \textit{Modern Compiler Implementation in ML} \cite{AppelAndrewW} and \cite{alma99122774374105763} is based on the following equations for the live-in and live-out variables respectively:
\begin{align}
  in\left[n\right] &= use\left[n\right] \cup (out\left[n\right] - \mathit{def}\left[n\right])\\
  out\left[n\right] &= \bigcup_{s\in \mathit{succ}\left[n\right]} in\left[s\right]
\end{align}
where \(use\left[n\right]\) is the set of all dependent variables, \(def\left[n\right]\) is the set of all variables defines and \(succ\left[n\right]\) is the set of all immediate successor nodes of \(n\).

The structure of the CFG is inherently vague as both   \cite{AppelAndrewW} and \textit{Compilers : Principles, Techniques, and Tools} \cite{alma99122774374105763}, while based on the same underlying % TODO: fix references
conceptions of dataflow, have different approaches to nodes of a CFG, with the former taking each individual instruction into consideration and the latter each basic block. Either of these approaches are sound

@@

\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 add & addx & \{\}\\
 \hline
 mul & imul & \{ \%rax \} \\
 \hline
 sdiv & idivx & \{\%rax, \%rdx\} \\
 \hline
 srem & idivx & \{\%rax, \%rdx \\
 \hline
   call & callx & \{\%rax, \textit{caller saved registers}\} \\
 \hline
 \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 fib & clang & greedy & briggs & linear \\ [0.5ex] 
 \hline
 40 & 1.000000 & 1.438693 & 1.441270 & 0.73 \\ [1ex] 
 41 & 1.000000 & 1.441035 & 1.440626 & 0.73 \\ [1ex] 
 \hline
\end{tabular}
\end{center}

bench clang	benches/fib.ll 42 	min=5494929992 (1.000000)	avg=5545852373 (1.000000)	max=5669289413
bench greedy	benches/fib.ll 42 	min=7951933724 (1.447140)	avg=7969947833 (1.437101)	max=8004638438
bench briggs	benches/fib.ll 42 	min=7946186345 (1.446094)

\begin{center}
\begin{tabular}{|c||c|c|c|c|} 
 \hline
 sha256 & clang & greedy & briggs & linear \\ [0.5ex] 
 \hline
 1000000 & 1 & 0.73 & 0.73 & 0.73 \\ [1ex] 
 \hline
\end{tabular}
\end{center}
